---
title: "Teeth for Comparisons V3"
author: "Bruce Wang"
date: "4/30/2019"
output: html_document
---

```{r setup, echo = FALSE,message=FALSE,error=FALSE,warning=FALSE}
setwd('/Users/brucewang/Dropbox (Princeton)/Data + Experiments Tim Sudijono/')
library(knitr)
library(rgl)
library(FNN)
library(pracma)
library(Rvcg)
library(Matrix)
load('chris_doug_analysis.Rdata')
setwd('/Users/brucewang/Dropbox (Princeton)/Data + Experiments Tim Sudijono/')
knit_hooks$set(webgl = hook_webgl)
```
# Prosminians (Comparisons 1 - 3)

## First comparison: Lepilemur (Top) vs Galago (Bottom)

```{r testgl, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}


mfrow3d(1,4)

setwd('/Users/brucewang/Dropbox (Princeton)/Data + Experiments Tim Sudijono/')

for (k in 1:length(list.files(pset1$dir1,full.names = TRUE))){
  mesh = vcgImport(list.files(pset1$dir1,full.names = TRUE)[k])
  plot3d(mesh, col = c1_mesh1_colors_list[[k]],back="lines", specular="black", axes = FALSE,xlab = '', ylab = '',zlab='')
  rgl.viewpoint(userMatrix = rotation_matrix)
}
#
#open3d()
#mfrow3d(2,4)
#
#for (k in 1:length(list.files(pset1$dir2,full.names = TRUE))){
#  mesh = vcgImport(list.files(pset1$dir2,full.names = TRUE)[k])
#  plot3d(mesh, col = c1_mesh2_colors_list[[k]],back="lines", specular="black", axes = FALSE,xlab = '', ylab = '',zlab='')
#  rgl.viewpoint(userMatrix = rotation_matrix)
#}


```

```{r testgl1.5, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}



open3d()
mfrow3d(2,4)

for (k in 1:length(list.files(pset1$dir2,full.names = TRUE))){
  mesh = vcgImport(list.files(pset1$dir2,full.names = TRUE)[k])
  plot3d(mesh, col = c1_mesh2_colors_list[[k]],back="lines", specular="black", axes = FALSE,xlab = '', ylab = '',zlab='')
  rgl.viewpoint(userMatrix = rotation_matrix)
}


```

## Second comparison: Varecia (Left) vs Lepilemur (Right)



```{r testgl2, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}

mfrow3d(1,4)

setwd('/Users/brucewang/Dropbox (Princeton)/Data + Experiments Tim Sudijono/')

for (k in 1:length(list.files(pset2$dir1,full.names = TRUE))){
  mesh = vcgImport(list.files(pset2$dir1,full.names = TRUE)[k])
  plot3d(mesh, col = c1_mesh1_colors_list[[k]],back="lines", specular="black", axes = FALSE,xlab = '', ylab = '',zlab='')
  rgl.viewpoint(userMatrix = rotation_matrix)
}
#
#open3d()
#mfrow3d(2,4)
#
#for (k in 1:length(list.files(pset2$dir2,full.names = TRUE))){
#  mesh = vcgImport(list.files(pset2$dir2,full.names = TRUE)[k])
#  plot3d(mesh, col = c1_mesh2_colors_list[[k]],back="lines", specular="black", axes = FALSE,xlab = '', ylab = '',zlab='')
#  rgl.viewpoint(userMatrix = rotation_matrix)
#}
```

## Third comparison: Varecia (Left) vs Tarsius (Right)




```{r testgl3, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}

```


## Fourth comparison: Alouatta (Left) vs Ateles (Right)




```{r testgl4, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}

```

## Fifth comparison: Brachyteles (Left) vs Ateles (Right)


```{r testgl5, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}

```
## Sixth comparison: Alouatta (Left) vs Brachyteles (Right)


```{r testgl6, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
```
## Seventh comparison: Callicebus (Left) vs Saimiri (Right)


```{r testgl7, webgl=TRUE,echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
```
